How to use replication assignments for teaching integrity in empirical archaeology

### 2019-06-20 README.Rmd
docker hub

# Teaching replication in archaeology
<!-- badges: start -->
[![Launch Rstudio Binder](http://mybinder.org/badge.svg)](https://mybinder.org/v2/gh/benmarwick/replicationteachingarchaeology/master?urlpath=rstudio) 
[![Travis-CI Build Status](https://travis-ci.org/benmarwick/replicationteachingarchaeology.svg?branch=master)](https://travis-ci.org/benmarwick/replicationteachingarchaeology)
<!-- badges: end -->

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/DBSW9>

@@

> Marwick, B., L. Wang, R. Robinson, H. Loiselle, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/DBSW9>

@@

You can download the compendium as a zip from from this URL: </archive/master.zip>

Or you can install this compendium as an R package, replicationteachingarchaeology, from GitHub with:
### Licenses

>>>>

# Teaching replication in archaeology
<!-- badges: start -->
[![Launch Rstudio Binder](http://mybinder.org/badge.svg)](https://mybinder.org/v2/gh/benmarwick/replicationteachingarchaeology/master?urlpath=rstudio) 
[![Travis-CI Build Status](https://travis-ci.org/benmarwick/replicationteachingarchaeology.svg?branch=master)](https://travis-ci.org/benmarwick/replicationteachingarchaeology)
[![ORCiD](https://img.shields.io/badge/ORCiD-0000--0001--7879--4531-green.svg)](http://orcid.org/0000-0001-7879-4531)

<!-- badges: end -->

@@

> Authors, (2019). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/DBSW9>

@@

> Marwick, B., L. Wang, R. Robinson, H. Loiselle, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for "`r Title`"_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/DBSW9>

@@

You can download the compendium as a zip from from this URL: [master.zip](/archive/master.zip)

Or you can install this compendium as an R package, teachingreplicationinarchaeology, from GitHub with:

### Licenses
